CRUSE to Safe Cycling in Ireland

### 2023-09-20 paper.qmd
Back to html version

# Uncomment for formatted version
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super

>>>>

# # Uncomment for formatted version
# format:
#   elsevier-pdf:
#     keep-tex: true
#     journal:
#       name: Journal Name
#       formatting: preprint
#       model: 3p
#       cite-style: super
